\subsubsection*{Publications}

\bigskip \noindent
\textit{Dissertation (Approved by Committee)} 
\bigskip \noindent 

\begin{itemize}[align=left, labelwidth=3em,]
    \item[D.1] \textbf{Flathmann, C.} (February 2023). How to Make Agents and Influence Teammates: Understanding the Social Influence AI Teammates Have in Human-AI Teams. Committee: Nathan McNeese, Brian Dean, Eileen Kraemer, Brygg Ullmer, Laine Mears
\end{itemize}

\bigskip \noindent
\textit{Journal Articles}

\bigskip 
\begin{itemize}[align=left, labelwidth=3em,]
\setlength\itemsep{1em}





\item[JA.29] Lancaster, C., \textbf{Flathmann, C.}, O'Neill, T., Salas, E., \& McNeese, N.J. (2025). Preparing for Tomorrow’s Teamwork: Insights from eSports on How Human Expertise Shapes Training Needs for AI-Integrated Work. \textit{Journal of Organizational Behavior}. \\

\item[JA.28] Kot, S., Engineer, M., Gilman, E., Flathmann, C., Pradham, A., Dixon, E., Exploring The Role of Generative AI in Dementia Resilience Building Activities: Uncovering Opportunities and Challenges. \textit{ACM Transactions on Computer-Human Interaction} \\


%%%%%%% September 2025 Cutoff


\item[JA.27] \textbf{Flathmann, C.}, McNeese, N.J., Sengupta, S., \& Johnson, E. (2025). Exploring Trust, Acceptance, and Behavioral Differences When Humans Collaborate with Large Language Models as Tools and Teammates. \textit{ACM Transactions on Interactive Intelligent Systems}. \\

\item[JA.26] Hauptman, A.I., Schelble, B.G., \textbf{Flathmann, C.}, Mallick, R. \& McNeese, N.J.(2025). Ethical Adaptation: Exploring the Use of Adaptive Autonomy in the Design of Ethical AI Teammates in Healthcare. AI and Ethics. \\

\item[JA.25] \textbf{Flathmann, C.}, McNeese, N. J., \& O’Neill, T. A. (2025). Designing High-Impact Experiments for Human–Autonomy/AI Teaming. Journal of Cognitive Engineering and Decision Making, 15553434251327697. \url{https://doi.org/10.1177/15553434251327697}

\item[JA.24] Zhang, R., Duan, W., \textbf{Flathmann, C.}, McNeese, N., Knijnenburg, B., \& Freeman, G. (2024). Verbal vs. Visual: How Humans Perceive and Collaborate with AI Teammates Using Different Communication Modalities in Various Human-AI Team Compositions. Proceedings of the ACM on Human-Computer Interaction, 8(CSCW2), 1-34. \url{https://doi.org/10.1145/3686976}

\item[JA.23] Sengupta, S., \textbf{Flathmann, C.}, Schelble, B., Lyons, J. B., \& McNeese, N. (2024). An analysis of ethical rationales and their impact on the perceived moral persona of AI teammates. AI and Ethics, 1-13. \url{https://doi.org/10.1007/s43681-024-00515-5}

\item[JA.22] Schelble, B. G., \textbf{Flathmann, C.}, Macdonald, J. P., Knijnenburg, B., Brady, C., \& McNeese, N. J. (2024). Modeling perceived information needs in human-AI teams: improving AI teammate utility and driving team cognition. Behaviour \& Information Technology, 1–24. \url{https://doi.org/10.1080/0144929X.2024.2396476}

\item[JA.21] Mallick, R., \textbf{Flathmann, C.}, Duan, W., Schelble, B. G., \& McNeese, N. J. (2024). What you say vs what you do: Utilizing positive emotional expressions to relay AI teammate intent within human-AI teams. \textit{International Journal of Human-Computer Studies}, 103355. 
\url{https://doi.org/10.1016/j.ijhcs.2024.103355}

\item[JA.20] Hauptman, A. I., Mallick, R., \textbf{Flathmann, C.}, \& McNeese, N. J. (2024). Human factors considerations for the context-aware design of adaptive autonomous teammates. \textit{Ergonomics}, 1-17.
\url{https://doi.org/10.1080/00140139.2024.2380341}

\item[JA.19] Hauptman, A. I., \textbf{Flathmann, C.}, \& McNeese, N. J. (2024). Adapting to the human: A systematic review of a decade of human factors research on adaptive autonomy. \textit{Applied Ergonomics}, 120, 104336. \url{https://doi.org/10.1016/j.apergo.2024.104336}

\item[JA.18] Hauptman, A. I., Schelble, B. G., Duan, W., \textbf{Flathmann, C.}, \& McNeese, N. J. (2024). Understanding the influence of AI autonomy on AI explainability levels in human-AI teams using a mixed methods approach. \textit{Cognition, Technology \& Work}, 1-21. \url{https://doi.org/10.1007/s10111-024-00765-7}\\

\item[JA.17] \textbf{Flathmann, C.}, Duan, W., McNeese, N., Hauptman, A., \& Zhang, R. (2024). Empirically Understanding the Potential Impacts and Process of Social Influence in Human-AI Teams. \textit{Proceedings of the ACM on Human-Computer Interaction.} (CSCW). \url{https://doi.org/10.1145/3637326}\\

\item[\faTrophy JA.16] Zhang, R., \textbf{Flathmann, C.}, Duan. W., Schelble, B.G., McNeese, N.J., \& Knijnenberg, B. (2024). I Know This Looks Bad, But I Can Explain: Understanding When AI Should Explain Actions In Human-AI Teams. \textit{ACM Transactions on Interactive Intelligent Systems}. \url{http://dx.doi.org/10.1145/3635474} \\\textbf{*Recognized as Feature Paper by TIIS}\\

\item[JA.15] O’Neill, T. A., \textbf{Flathmann, C.}, McNeese, N. J., Jones, S. K., \& Schelble, B. (2024). A comment on “Can you Outsmart the Robot? An Unexpected Path to Work Meaningfulness” by Bernadeta Goštautaitė, Irina Liubertė, Sharon K. Parker, and Ilona Bučiūnienė: Calling for a different path for the future of human-robot teaming. \textit{Academy of Management Discoveries.} \url{https://doi.org/10.5465/amd.2024.0009}\\

\item[JA.14] Musick, G., Duan, W., Sengupta, S., \textbf{Flathmann, C.}, Knijnenburg, B., \& McNeese, N.J., (2024). To share or not to share: Understanding and modeling individual disclosure preferences in recommender systems for the workplace. \textit{ACM GROUP}. \url{https://doi.org/10.1145/3633074}\\

\item[JA.13] Lancaster, C., Schulenberg, K., \textbf{Flathmann, C.}, McNeese, N.J., \& Freeman, G., (2024). "It's Everybody's Role to Speak Up... But Not Everyone Will": Understanding AI Professionals' Perceptions of Accountability for AI Bias Mitigation. \textit{ACM Responsible Computing}. \url{https://doi.org/10.1145/3632121}\\

\item[JA.12] Musick, G., Hauptman, A. I., \textbf{Flathmann, C.}, McNeese, N. J., \& Knijnenburg, B. P. (2023). Recommendations with Benefits: Exploring Explanations in Information Sharing Recommender Systems for Temporary Teams. \textit{International Journal of Human-Computer Interaction} \url{https://doi.org/10.1080/10447318.2023.2278933}\\

\item[JA.11] Mallick, R., \textbf{Flathmann, C.}, Lancaster, C., Hauptman, A., McNeese, N.J., \& Freeman, G., (2023). The pursuit of happiness: the power and influence of AI teammate emotion in human-AI teamwork \textit{Behavior and Information Technology}. \url{https://doi.org/10.1080/0144929X.2023.2277909}\\

\item[JA.10] \textbf{Flathmann, C.}, Schelble, B.G., McNeese, N.J., Knijnenberg, B., Gramopadhye, A., \& Madathil K.C. (2023). The Purposeful Presentation of AI Teammates: Impacts on Human Acceptance and Perception. \textit{International Journal of Human-Computer Interaction}. \url{https://doi.org/10.1080/10447318.2023.2254984}\\

\item[JA.9] Mcneese, N.J., \textbf{Flathmann, C.}, O'Neill, T., \& Salas, E., (2023). Stepping out of the shadow of human-human teaming: Crafting a unique identity for human-autonomy teams \textit{Computers in Human Behavior}. \url{https://doi.org/10.1016/j.chb.2023.107874}\\

\item[JA.8] O'Neill, T., \textbf{Flathmann, C.}, McNeese, N.J., \& Salas, E., (2023). 21st Century teaming and beyond: Advances in human-autonomy teamwork \textit{Computers in Human Behavior}. \url{https://doi.org/10.1016/j.chb.2023.107865}\\

\item[JA.7] \textbf{Flathmann, C.}, Schelble, B. G., Rosopa, P. J., McNeese, N. J., Mallick, R., \& Madathil, K. C. (2023). Examining the impact of varying levels of AI teammate influence on human-AI teams. \textit{International Journal of Human-Computer Studies}, 177, 103061. \url{https://doi.org/10.1016/j.ijhcs.2023.103061} \\

\item[JA.6] O'Neill, T., \textbf{Flathmann, C.}, McNeese, N.J., \& Salas, E., (2023). Human-autonomy Teaming: Need for a guiding team-based framework? \textit{Computers in Human Behavior}. \url{https://doi.org/10.1016/j.chb.2023.107762}\\

\item[JA.5] Zhang, R., Wen, D., \textbf{Flathmann, C.}, Freeman, G., \& McNeese, N.J. (2023). Investigating AI Teammate’s Communication Strategies and Their Impact in Human-AI Teams For Effective Teamwork. \textit{Proceedings of the ACM on Human-Computer Interaction.} (CSCW). \url{https://doi.org/10.1145/3610072} \\

\item[JA.4] \textbf{Flathmann, C.}, McNeese, N.J., Schelble, B.G., Knijnenburg, B., \& Freeman, G. (2023). Understanding the Impact and Design of AI Teammate Etiquette. \textit{Human-Computer Interaction}. \url{https://doi.org/10.1080/07370024.2023.2189595}\\

\item[JA.3] Schelble, B., \textbf{Flathmann, C.}, McNeese, N.J., O'Neill, T., Pak, R., \& Namara, M. (2022). Investigating the Effects of Perceived Teammate Artificiality on Human Performance and Cognition. \textit{International Journal of Human-Computer Interaction}. \url{https://doi.org/10.1080/10447318.2022.2085191}\\

\item[JA.2] Schelble, B.G., \textbf{Flathmann, C.}, Musick, G., McNeese, N.J., \& Freeman, G. (2022). I See You: Examining the Role of Spatial Information in Human-Agent Teams. \textit{Proceedings of the ACM on Human-Computer Interaction.} (CSCW), 1-27. \url{https://doi.org/10.1145/3555099}\\

\item[\faTrophy \hspace{1pt} JA.1] Schelble, B.G., \textbf{Flathmann, C.}, McNeese, N.J., Freeman, G., \& Mallick, R. (2022). Let's Think Together! Assessing Shared Mental Models, Performance, and Trust in Human-Agent Teams. \textit{Proceedings of the ACM on Human-Computer Interaction.} \textit{6}(GROUP), 1-29. \url{https://doi.org/10.1145/3492832} \textbf{*Honorable Mention Paper Award} \\

\end{itemize}


\bigskip \noindent
\textit{Book Chapters:} 
\bigskip \noindent

\begin{itemize}[align=left, labelwidth=3em,]
\setlength\itemsep{1em}

\item[B.3] Sengupta, S., Wen, D., \textbf{Flathmann, C.}, \& McNeese, N. J. (in press). Sustaining human-AI collaboration: Exploring the interplay between ethics and trust. In T. Reimer, L. van Swol., \& A. Florack (Eds.), The Routledge Handbook of Communication and Social Cognition. Routledge/Taylor and Francis.

\item[B.2] \textbf{Flathmann, C.}, Schelble, B.G., \& McNeese, N.J. (2023). Refocusing Human-AI Interaction Through a Teamwork Lens. Book Chapter in \textit{Handbook on Virtual Work}. Edward Elgar Publishing. \url{https://doi.org/10.4337/9781802200508.00013}\\

\item[B.1] Rapa, L. J., Marshall, J. C., Madison, S. M., \textbf{Flathmann, C.}, Knijnenburg, B. P., \& McNeese, N. J. (2022). Clemson University's Teacher Learning Progression Program: Personalized Advanced Credentials for Teachers. In \textit{Handbook of Research on Credential Innovations for Inclusive Pathways to Professions} (pp. 313-334). IGI Global. \url{http://doi.org/10.4018/978-1-7998-3820-3.ch016} \\

\end{itemize}

\bigskip \noindent
\textit{Conference Full Papers (Referred):} 
\bigskip \noindent

\begin{itemize}[align=left, labelwidth=3em,]
\setlength\itemsep{1em}

\item[C.20] Duan, W., \textbf{Flathmann, C.}, McNeese, N., Scalia, M. J., Zhang, R., Gorman, J., ... \& Yin, X. (2025, April). Trusting Autonomous Teammates in Human-AI Teams-A Literature Review. In Proceedings of the 2025 CHI Conference on Human Factors in Computing Systems (pp. 1-23). \\

\item[C.19] Schelble, B. G., Filer, G., \textbf{Flathmann, C.}, \& Chalil Madathil, K. (2025). Examining the Role of AI Information-Sharing on Trust in Human-AI Teams. Proceedings of the Human Factors and Ergonomics Society Annual Meeting, 0(0). \url{https://doi.org/10.1177/10711813251367726} \\

\item[C.18] Wang, Y., Nguyen, H., Mallick, R., Andre, K., Duan, W., McNeese, N., \& \textbf{Flathmann, C.} (2015). A Framework Considering the Cross-Effects of Human and AI Collaboration on Team Resilience. In Proceedings of the Human Factors and Ergonomics Society Annual Meeting (p. 10711813251358241). Sage CA: Los Angeles, CA: SAGE Publications. \\

\item[C.17] Basappa, R., Lancaster, C., Mallick, R., \textbf{Flathmann, C.}, \& McNeese, N. (2025). Mind the Gaps: How AI Shortcomings and Human Concerns May Disrupt Team Cognition in Human-AI Teams (HATs). Proceedings of the Human Factors and Ergonomics Society Annual Meeting, 0(0). \url{https://doi.org/10.1177/10711813251361002} \\


\item[C.16] \textbf{Flathmann, C.}, Schelble, B., \& Ihekweazu, C. (2025). Leveraging Generative AI to Create Lightweight Simulations for Far-Future Autonomous Teammates. Proceedings of the Human Factors and Ergonomics Society Annual Meeting, 0(0). \url{https://doi.org/10.1177/10711813251357885} \\


\item[C.15] Nguyen, H., Wang, Y., André, K., Duan, W., \textbf{Flathmann, C.}, \& McNeese, N. (2025). Modeling Adaptive Autonomy at the Team Level: Understanding Team-Wide Autonomy and its Impact on Situation Awareness in Human-Autonomy Teams. Proceedings of the Human Factors and Ergonomics Society Annual Meeting, 0(0). \url{https://doi.org/10.1177/10711813251358809} \\


\item[C.14] Guynup, C., Sawant, S., Delgado Solorzano, C., Arnold, E., Poe, A., \textbf{Flathmann, C.}, McNeese, N., Chalil Madathil, K., Toxtli Hernandez, C., \& Gramopadhye, A. (2025). Working in a Heartbeat: Considerations for AI Teammates in Search and Rescue Teams. Proceedings of the Human Factors and Ergonomics Society Annual Meeting, 0(0). \url{https://doi.org/10.1177/10711813251358806} \\


\item[C.13] Basappa, R., Mallick, R., Flathmann, C., \& McNeese, N. (2025). Unlocking Collective Potential: Modeling Creativity in Human-AI Teams. Proceedings of the Human Factors and Ergonomics Society Annual Meeting, 0(0). \url{https://doi.org/10.1177/10711813251358795} \\


\item[C.12] Hauptman, A. I., Schelble, B. G., \textbf{Flathmann, C.}, \& McNeese, N. J. (2024, May). The Role of Autonomy Levels and Contextual Risk in Designing Safer AI Teammates. In 2024 IEEE 4th International Conference on Human-Machine Systems (ICHMS) (pp. 1-7). IEEE. \\

\item[C.11] \textbf{Flathmann, C.}, Schelble, B. G., \& Galeano, A. (2024, August). Empirical Impacts of Independent and Collaborative Training on Task Performance and Improvement in Human-AI Teams. In Proceedings of the Human Factors and Ergonomics Society Annual Meeting (p. 10711813241274425). Sage CA: Los Angeles, CA: SAGE Publications.\\

\item[C.10] Guo, L., \textbf{Flathmann, C.}, Anaraky, R., McNeese, N., \& Knijnenburg, B. (2022) The Effect of Recommendation Source and Justification on Professional Development Recommendations for High School Teachers. \textit{HT’22: 33rd ACM Conference on Hypertext and Social Media}. \url{https://doi.org/10.1145/3511095.3531280}\\

\item[C.9] \textbf{Flathmann, C.}, Schelble, B. G., \& McNeese, N. J. (2021, September). Fostering Human-Agent Team Leadership by Leveraging Human Teaming Principles. \textit{In 2021 IEEE 2nd International Conference on Human-Machine Systems} (ICHMS) (pp. 1-6). IEEE. \url{https://doi.org/10.1109/ICHMS53169.2021.9582649}\\

\item[C.8] \textbf{Flathmann, C.}, Schelble, B. G., Zhang, R., \& McNeese, N. J. (2021, July). Modeling and Guiding the Creation of Ethical Human-AI Teams. \textit{In Proceedings of the 2021 AAAI/ACM Conference on AI, Ethics}, and Society (pp. 469-479). \url{https://doi.org/10.1145/3461702.3462573} \\

\item[\faTrophy C.7] Schelble, B., \textbf{Flathmann, C.}, Canonico, L. B., \& Mcneese, N. (2021, January). Understanding human-AI cooperation through game-theory and reinforcement learning models. \textit{In Proceedings of the Annual Hawaii International Conference on System Sciences}. \textit{Nominated for Best Paper} \url{http://dx.doi.org/10.24251/HICSS.2021.041} \\

\item[\faTrophy C.6] \textbf{Flathmann, C.}, Schelble, B., Tubre, B., McNeese, N., \& Rodeghero, P. (2020, November). Invoking Principles of Groupware to Develop and Evaluate Present and Future Human-Agent Teams. \textit{In Proceedings of the 8th International Conference on Human-Agent Interaction} (pp. 15-24). \textit{Awarded Overall Best Paper} \url{https://doi.org/10.1145/3406499.3415072} \\

\item[C.5] Schelble, B. G., \textbf{Flathmann, C.}, \& McNeese, N. (2020, November). Towards meaningfully integrating human-autonomy teaming in applied settings. \textit{In Proceedings of the 8th International Conference on Human-Agent} Interaction (pp. 149-156). \url{https://doi.org/10.1145/3406499.3415077} \\

\item[C.4] Musick, G., Maloney, D., \textbf{Flathmann, C.}, McNeese, N. J., \& Walton, J. (2020, December). Differentiated Instruction further Realized through Teacher-Agent Teaming. \textit{In Proceedings of the Human Factors and Ergonomics Society Annual Meeting} (Vol. 64, No. 1, pp. 1318-1322). Sage CA: Los Angeles, CA: SAGE Publications. \url{https://doi.org/10.1177\%2F1071181320641315} \\

\item[C.3] \textbf{Flathmann, C.}, McNeese, N., \& Canonico, L. B. (2019, November). Using human-agent teams to purposefully design multi-agent systems. \textit{In Proceedings of the Human Factors and Ergonomics Society Annual Meeting} (Vol. 63, No. 1, pp. 1425-1429). Sage CA: Los Angeles, CA: SAGE Publications. \url{https://doi.org/10.1177\%2F1071181319631238} \\

\item[C.2] Canonico, L. B., \textbf{Flathmann, C.}, \& McNeese, N. (2019, November). Collectively intelligent teams: Integrating team cognition, collective intelligence, and ai for future teaming. \textit{In Proceedings of the Human Factors and Ergonomics Society Annual Meeting} (Vol. 63, No. 1, pp. 1466-1470). Sage CA: Los Angeles, CA: SAGE Publications. \url{https://doi.org/10.1177\%2F1071181319631278} \\

\item[C.1] Canonico, L. B., \textbf{Flathmann, C.}, \& McNeese, N. (2019, November). The wisdom of the market: Using human factors to design prediction markets for collective intelligence. \textit{In Proceedings of the Human Factors and Ergonomics Society Annual Meeting} (Vol. 63, No. 1, pp. 1471-1475). Sage CA: Los Angeles, CA: SAGE Publications. \url{https://doi.org/10.1177\%2F1071181319631282} \\

\end{itemize}

\bigskip \noindent
\textit{Workshop Papers \& Organization (Peer Reviewed):}
\bigskip \noindent

\begin{itemize}[align=left, labelwidth=3em,]
\setlength\itemsep{1em}

\item[WP.4] \textbf{Christopher Flathmann,}, and Nathan J. McNeese (2022). Understanding the Criticality of Human Adaptation when Designing Human-Centered AI Teammates \textit{2022 NuerIPS workshop on Human-Centered Artificial Intelligence} Virtual, December 9, 2022. \\

\item[WP.3] Beau G. Schelble, \textbf{Christopher Flathmann,}, Scalia, M., Zhou, S., Chris Myers, Nathan J. McNeese, Jamie Gorman, Guo Freeman (2022). Addressing the Spread of Trust and Distrust in Distributed Human-AI Teaming Constellations. Workshop on Trust and Reliance in AI-Human Teams (TRAIT). \textit{2022 ACM Conference on Computer-Human Interaction (CHI'22).} New Orleans, LA. April 30th, 2022. \\

\item[WP.2] Guo, L., Anaraky, R., \textbf{Flathmann, C.}, McNeese, N.J., Knijnenburg, B. (2021). How to Recommend Professional Development Pathways to High School Teachers. Workshop on Human-Machine Partnerships in the Future of Work: Exploring the Role of Emerging Technologies in Future Workplaces. \textit{2021 ACM Conference on Computer Supported Cooperative Work (CSCW'21).} Virtual. Oct. 23rd, 2021. \\

\item[WP.1] Schelble, B.G., \textbf{Flathmann, C.}, McNeese, N.J. (2021). Reducing Bias by Prioritizing Multi-Cultural Human-Agent Teams. Workshop on Human-Machine Partnerships in the Future of Work: Exploring the Role of Emerging Technologies in Future Workplaces. \textit{2021 ACM Conference on Computer Supported Cooperative Work (CSCW'21).} Virtual. Oct. 23rd, 2021.

\end{itemize}

\bigskip \noindent
\textit{Research Posters:}
\bigskip \noindent

\begin{itemize}[align=left, labelwidth=3em,]
\setlength\itemsep{1em}

\item[P.2] \textbf{Flathmann, C.}, Schelble, B.G., \& McNeese, N.J. (2020, September). Creating Human-Oriented Multi-Agent Teams. In \textit{Insights @ BMW Manufacturing Co. LLC.} Greenville, SC. \\

\item[P.1] \textbf{Flathmann, C.} and Nathan McNeese. 2020. Using Human-Agent Teams to Purposefully Design Multi-Agent Teams. \textit{Clemson 2019 Research Symposium}, 12 April 2019 \\

\end{itemize}

\bigskip \noindent
\textit{Presentations (Invited, Conference, \& Program Reviews):}
\bigskip \noindent

\begin{itemize}[align=left, labelwidth=3em,]
\setlength\itemsep{1em}

\item[PRE.19] Future Applications of Human-AI Interaction. George Washington University. November 2025 \\

\item[PRE.18] Rethinking Human-in-the-Loop. South Carolina Center of AI Excellence. June 2025 \\

\item[PRE.17] Understanding the Future of Humans and AI Technology. Easley Chamber of Commerce Keynote. May 2025 \\

\item[PRE.16] Understanding Human-AI Teaming. Rice University. March 2025 \\

\item[PRE.15] Leveraging AI Technology for Social Good and Mobility. Clemson University, Brooke T. Smith Launchpad. March 2025. \\

\item[PRE.14] Understanding the Impact of Trust and Ethics in Human-Autonomy Teaming. AFOSR Trust and Influence Annual Program Review Meeting. August 2025. \\

\item[PRE.13] Leveraging The Capabilities and Limitations of Human-Autonomy Teams to Overcome High-Risk Environments. ONR Science of Autonomy Annual Program Review Meeting. August 2025. \\

\item[PRE.12] Understanding the Impact of Trust and Ethics in Human-Autonomy Teaming. AFOSR Trust and Influence Annual Program Review Meeting. August 2024. \\

\item[PRE.11] Introducing Clemson University's New AI Entrepreneur Competition on AI for Social Good. Clemson University. March 2024. \\

\item[PRE.10] Understanding how Robotics will Evolve the Future of Teamwork. HCC 8500. Janurary 2024

\item[PRE.9] Leveraging AI Technology as a Key Component of Future Manufacturing Strategies. AMFG 6800. October 2023. \\

\item[PRE.8] Understanding the Impact of Trust and Ethics in Human-Autonomy Teaming. AFOSR Trust and Influence Annual Program Review Meeting. September 2022. \\

\item[PRE.7] Reshaping Human Roles in Future Smart Manufacturing Environments. AMFG 6800. September 2022. \\



\item[PRE.6] Connecting and Leveraging Physical and Digital Dimensions to Advance Human-Autonomy Teaming. ONR Science of Autonomy Annual Program Review Meeting. September 2022. \\

\item[PRE.5] The role of AI in Future Manufacturing Environments. AMFG 6800. September 2021. \\

\item[PRE.4] Fostering Human-Agent Team Leadership by Leveraging Human Teaming Principles. IEEE ICHMS. September 2021. \\

\item[PRE.3] Contributing to the NRT Structure and Content. NRT Annual Meeting. January 2021. \\

\item[PRE.2] Invoking Principles of Groupware to Develop and Evaluate Present and Future Human-Agent Teams. Human-Agent Interaction. October 2020. \\

\item[PRE.1] Using Human-Agent Teams to Purposefully Design Multi-Agent Systems. Human Factors and Ergonomics Society Annual Meeting. November 2019.

\end{itemize}


\bigskip \noindent
\textit{News Coverage:}
\bigskip \noindent


\begin{itemize}[align=left, labelwidth=3em,]
\setlength\itemsep{1em}


  \item [N.11] How Polite Should You Be to AI?. 2025. Indeed.com
  \item [N.10] How AI Can Help Humans Work Together—Or Drive Us Apart. 2025. Complete AI Training.
  \item [N.9] Graduate returns to Clemson to shape the future of AI. 2025. Clemson News.
  \item [N.8] ‘Fierce Five’ power the future of higher education. 2025. Clemson News.
  \item [N.7] Researchers tackle a crucial question: What happens when humans clash with AI – and each other? 2025. Clemson News.
  \item [N.6] Clemson graduates first class of Breakthrough Scholars. 2025. Clemson News.
  \item [N.5] How Clemson University used Prolific to explore human-AI collaboration. 2024. Prolific.
  \item [N.4] Clemson student clones Fox Carolina News anchor’s voice using AI. 2024. Fox Carolina.
  \item [N.3] Do You Need a Chatbot for Work Meetings? 2023. Associations Now.
  \item [N.2] Closing the skills gap in the manufacturing workforce. 2022. Clemson News.
  \item [N.1] Artificial intelligence could one day be your teammate. 2021. Clemson News.

\end{itemize}

